### 2023-08-30 appendixPN.tex
up

For the sake of clarity \alain{bof, une autre raison?}, we will use reset Petri nets \cite{dufourd1998reset} rather than reset-VASS.

>>>>

For the sake of clarity \alain{bof, une autre raison?}\mathieu{for better visualisation? better representation?}, we will use reset Petri nets \cite{dufourd1998reset} rather than reset-VASS.
